Accuracy, Stability, and Efficiency of Lattice Boltzmann Models in Simulating Non-Newtonian Flow

### 2016-04-29 main.tex
Began numerical study section

\section{Numerical Study}

\subsection{Poiseuille Flow}

\subsection{Lid-driven Flow}

>>>>

\section{Numerical Study}
Two different flow simulations, Poiseuille flow and lid-driven flow, and two different non-Newtonian behaviors, yield stress fluids and power-law fluids,  served as the basis for the numerical study. 
\subsection{Poiseuille Flow} 
Computational Efficiency

Numerical Stability
\subsection{Lid-driven Flow}
Lid-driven cavity flow was simulated using Bingham numbers of 1, 10, and 100 for Reynolds numbers of 100, 1000, 5000, and 10000.  In the simulations, a constant velocity of $u_0$ was fixed at 0.1 across the lid.  No slip boundary conditions were fixed to the remaining walls of the cavity.  To validate the model used for the comparison, the results had to be compared with results from [...,...,...].  As shown in the table, it can be seen that the results of the present simulations match the benchmark results well (hopefully).

Computational Efficiency/Time

Numerical Stability

Effect of entropic filtering

Effect of m (stress growth exponent)
